---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# cartofr

The goal of cartofr is to provides a set of data to plot French administrative system

## Installation

You can install the released version of cartofr from [Github](https://github.com/denrou/cartofr) with:

```{r install, eval=FALSE}
remotes::install_github("denrou", "cartofr")
```

## Data

To get data from the package, just use:

```{r import}
data("cartofr")
```

`cartofr` is a list of 4 datasets in a `sf` format (links provide the source of the dataset):

+ [country](https://data.opendatasoft.com/explore/dataset/countries-codes@public/information/?lang=fr) The external border of France.
+ [region](https://data.opendatasoft.com/explore/dataset/regions-francaises-openstreetmap@public/information/?lang=fr) The name and code of French regions.
+ [dept](https://data.opendatasoft.com/explore/dataset/geoflar-departements-2015@public/information/?lang=fr) The name and code of French departments.
+ [insee](https://data.opendatasoft.com/explore/dataset/code-postal-code-insee-2015@public/information/?lang=fr) The name and code of French towns.

## Plots

This package doesn't provide any plot functions, but since objects are `sf`, it is pretty straigtforward to plot them either using `ggplot2` or `leaflet`.


```{r ggplot}
# Using ggplot2
library(ggplot2)
library(sf)
ggplot() + 
  geom_sf(data = cartofr[["region"]]) + 
  geom_sf_label(aes(label = name_fr), data = suppressWarnings(st_centroid(cartofr[["region"]])), size = 2.5) + 
  theme_void()
```

```{r leaflet, eval=FALSE}
# Using leaflet
library(leaflet)
cartofr[["dept"]] %>% 
  leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(label = ~name_fr, color = "gray", opacity = 1, fillOpacity = 0, weight = 2)
```
